OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2021-10-25 paper/paper.Rmd
Use msphere csl
it turns out that it's the same as the msystems csl

---
title: "OptiFit: an improved method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
link-citations: true
output:
  pdf_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: yes
  github_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    html_preview: false
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
params:
    snakemake: "none"
---

@@

figures_meta <- yaml::read_yaml(here('config', 'figures.yaml'))
figs <- function(fig_name, attribute) {
  value <- figures_meta[[fig_name]][[attribute]]
  if (attribute == 'cap') {
    value <- glue("\\label{fig:[fig_name]}[value]", .open='[', .close = ']')
  } else {
    value <- eval(parse(text = value))
  }
  return(value)
}

>>>>

---
title: "OptiFit: an improved method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
link-citations: true
output:
  pdf_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: yes
  github_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    html_preview: false
csl: msphere.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
params:
    snakemake: "none"
---

@@

figures_meta <- yaml::read_yaml(here('paper', 'figures.yaml'))
figs <- function(fig_name, attribute) {
  value <- figures_meta[[fig_name]][[attribute]]
  if (attribute == 'cap') {
    value <- glue("\\label{fig:[fig_name]}[value]", .open='[', .close = ']')
  } else {
    value <- eval(parse(text = value))
  }
  return(value)
}
